@mvreference{
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\title{\Huge AETHER \\ \Large Volume I: Expanded Compliance Modules}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Expanded Compliance Modules}

\subsection*{1. Newton’s Gravity Reproduced}
\[
\vec{F} = m \nabla P, \quad P(\vec{r}) = - \frac{G M}{r} \Rightarrow \vec{F} = - \frac{G M m}{r^2} \hat{r}
\]
This reproduces Newton’s inverse-square law via pressure gradients.

\subsection*{2. Einstein’s Curvature as Fluidic Field}
\[
R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R = \frac{8 \pi G}{c^4} T_{\mu\nu} \Rightarrow \text{Emerges as macroscopic tension in aetheric flow}
\]

\subsection*{3. Maxwell from Cymatics}
\[
\nabla \cdot \vec{E} = \frac{\rho}{\varepsilon_0}, \quad \nabla \cdot \vec{B} = 0, \quad \nabla \times \vec{E} = -\frac{\partial \vec{B}}{\partial t}
\]
Derived from harmonic wave behavior in Æ₀ substrate.

\subsection*{4. Schrödinger from Field Oscillation}
\[
i \hbar \frac{\partial \Psi}{\partial t} = -\frac{\hbar^2}{2m} \nabla^2 \Psi + V \Psi
\]
Wave mechanics arises from cymatic pressure fields.

\subsection*{5. Planck Constants Emergence}
\[
h, \quad \hbar = \frac{h}{2\pi} \quad \text{Define fundamental frequency/energy quantization: } E = hf
\]

\subsection*{6. Wave-Particle Duality as Cymatic Eigenmode}
\[
\lambda = \frac{h}{p} \Rightarrow \text{Standing waves in toroidal field manifest as particles}
\]

\subsection*{7. Uncertainty from Harmonic Phase}
\[
\Delta x \Delta p \geq \frac{\hbar}{2} \Rightarrow \text{Emerges from harmonic uncertainty}
\]

\subsection*{8. Light Speed as Propagation Velocity}
\[
c = \frac{1}{\sqrt{\mu_0 \varepsilon_0}} \Rightarrow \text{Speed of aetheric wave propagation}
\]

\subsection*{9. Galaxy Rotation via Aether Drag}
\[
v(r) \approx \text{constant} \Rightarrow \text{Due to pressure vortex, not dark matter}
\]

\subsection*{10. Dark Energy as Vacuum Pressure}
\[
P_{\text{vacuum}} = \rho_{\Lambda} c^2 \Rightarrow \text{Baseline aether tension expansion}
\]

\subsection*{11. Entropy from Toroidal Complexity}
\[
S = k_B \ln \Omega, \quad \Omega = \text{Toroidal microstates}
\]

\subsection*{12. Conservation from Symmetries}
\[
\frac{d}{dt} \int_V \rho \, dV = 0, \quad \frac{d}{dt} \int_V \vec{J} \, dV = 0
\]

\subsection*{13. CMB as Standing Aether Wave}
\[
T(k) \Rightarrow \text{Mode interference in aether substrate}
\]

\subsection*{14. Redshift via Pressure Gradient}
\[
z = \frac{\lambda_{\text{obs}} - \lambda_{\text{emit}}}{\lambda_{\text{emit}}} \Rightarrow \text{Aether field dilation}
\]

\subsection*{15. Black Hole via Pressure Sink}
\[
\Phi_{\text{black}} = -\nabla P, \quad \text{Collapse into null-toroidal field}
\]

\subsection*{16. Unified Lagrangian Formalism}
\[
\mathcal{L}_{\text{Aether}} = \frac{1}{2} \rho_{\text{eff}} \dot{\Phi}^2 - \frac{1}{2} \kappa_{\text{res}}(\Phi^2 + |\Psi|^2) + \sum \lambda_n |\nabla C|^2 + m \nabla P
\]

\subsection*{17. Gauge Symmetry via Harmonics}
\[
\mathcal{U}(1), SU(2), SU(3) \Rightarrow \text{Harmonic eigenmodes in toroidal cymatic field}
\]

\subsection*{18. Locality Preserved through Resonance}
\[
\text{Field propagation constrained by } c, \quad \text{Information travels as phase shift}
\]

\subsection*{19. Equivalence from Field Tension}
\[
F = m \nabla P \Rightarrow \text{Inertial and gravitational mass equivalent through field tension}
\]

\subsection*{20. General Covariance via Phase Independence}
\[
\mathcal{L} \text{ invariant under } \phi \rightarrow \phi + \delta\phi \Rightarrow \text{Coordinate-free formalism}
\]

\end{document}
,
	editor = {editor},
	title = {title},
	date = {date},
	OPTeditora = {editora},
	OPTeditorb = {editorb},
	OPTeditorc = {editorc},
	OPTtranslator = {translator},
	OPTannotator = {annotator},
	OPTcommentator = {commentator},
	OPTintroduction = {introduction},
	OPTforeword = {foreword},
	OPTafterword = {afterword},
	OPTsubtitle = {subtitle},
	OPTtitleaddon = {titleaddon},
	OPTlanguage = {language},
	OPToriglanguage = {origlanguage},
	OPTedition = {edition},
	OPTvolumes = {volumes},
	OPTseries = {series},
	OPTnumber = {number},
	OPTnote = {note},
	OPTpublisher = {publisher},
	OPTlocation = {location},
	OPTisbn = {isbn},
	OPTpagetotal = {pagetotal},
	OPTaddendum = {addendum},
	OPTpubstate = {pubstate},
	OPTdoi = {doi},
	OPTeprint = {eprint},
	OPTeprintclass = {eprintclass},
	OPTeprinttype = {eprinttype},
	OPTurl = {url},
	OPTurldate = {urldate},
}
