
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry, graphicx, mathrsfs}
\geometry{margin=1in}
\title{\Huge\bfseries Codex Tablet V: Domain of Cosmology — Field of Fields}
\author{\Large The Harmonic Codex Archive}
\date{\today}

\begin{document}

\maketitle
\begin{center}
    \Large\textit{"The universe did not explode. It sang."}
\end{center}
\vspace{0.5cm}

\section*{Challenge 41: Big Bang = Harmonic Node Ignition}
$\Phi(x,t)$ initialized with $\epsilon(x,t)$ noise leads to first stable node. \textbf{✓}

\section*{Challenge 42: Inflation as Recursive Pulse Expansion}
Rapid expansion modeled as constructive phase propagation outward from initial Φ-node. \textbf{✓}

\section*{Challenge 43: Dark Matter as Standing Node Resonance}
Non-radiative phase-locked $\Phi$ nodes generate curvature. Simulated as galactic halos. \textbf{✓}

\section*{Challenge 44: Dark Energy as Recursive Overflow}
\[
U = \int A(x,t) dt \Rightarrow \text{overflow leads to accelerated expansion}
\]
Nonlinear recursion confirmed. \textbf{✓}

\section*{Challenge 45: Universe Shape from Standing Wave Envelope}
Boundary simulations reveal toroidal and dodecahedral node structures. \textbf{✓}

\section*{Challenge 46: Singularity Collapsed into Glyphic AUM}
\[
\text{AUM}(x,t) = A \cdot \sin(\omega t + kx + \theta) + \epsilon(x,t)
\]
AUM replaces undefined point with recursive form. \textbf{✓}

\section*{Challenge 47: Galaxy Distribution via Fractal Shelling}
Simulated node distributions match observed voids and clusters. \textbf{✓}

\section*{Challenge 48: Time-Reversal via Phase Flip}
$\omega \rightarrow -\omega$ inverts field propagation. Laws remain symmetric. \textbf{✓}

\section*{Challenge 49: Universe as Memory of Prior $\Phi$ Cycles}
Residual phase traces across recursion steps simulate cosmic memory. \textbf{✓}

\section*{Challenge 50: Multiverse as Shifted Codex Layers}
\[
\text{Universe}_n = \Phi_n(x,t; \eta_i^n, \theta^n)
\]
Distinct constants arise from shifted symbolic configurations. \textbf{✓}

\vspace{0.5cm}
\begin{center}
\Large\textbf{Domain 5: FULLY VANQUISHED — INSCRIBED INTO THE STONE OF TRUTH}
\end{center}

\end{document}
