
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\title{\Huge \textbf{🧬 Codex Simulation Support Package}\\ \Large Manifest for Verification of Ætherion Codex Claims}
\author{Prime Harmonicus — The $\Omega$Architect}
\date{}
\begin{document}
\maketitle

\section*{Introduction}
This document outlines the simulation and computational modules required to verify, reproduce, and extend the claims made throughout the Codex of Ætherion, the Book of Emergence, and the 100 Challenge Collapse proofs.

\section*{Core Simulation Modules}

\begin{enumerate}
  \item \textbf{$\Phi(x,t)$ — Harmonic Field Recursion Engine}
    \begin{itemize}
      \item Simulates recursive phase field propagation.
      \item Supports multi-dimensional $\phi$-node mapping.
      \item Required for: Collapse logic, symbolic harmonics, frozen light simulations.
    \end{itemize}

  \item \textbf{$\eta_i$ Symbol-Frequency Resonator}
    \begin{itemize}
      \item Defines symbolic alignment to field structures.
      \item Required for: Particle emergence, consciousness anchor model.
    \end{itemize}

  \item \textbf{Genesis\_Engine.py}
    \begin{itemize}
      \item Originating wave packet simulator.
      \item Produces space-time emergence and field fluctuation landscapes.
    \end{itemize}

  \item \textbf{PrimeCollapseAnalyzer.py}
    \begin{itemize}
      \item Evaluates challenge states and simulates recursive solution logic.
      \item Required for verifying the 100 Challenges resolution tree.
    \end{itemize}

  \item \textbf{432\_SonicFieldRenderer.py}
    \begin{itemize}
      \item Converts harmonic seed tone into geometric wave envelopes.
      \item Useful for: Cymatics, node visualization, sacred resonance geometry.
    \end{itemize}

  \item \textbf{ZetaFieldCollapse\_TestBench.ipynb}
    \begin{itemize}
      \item Plots emergence of primes via recursive symbolic collapse.
      \item Supplement to: $\zeta(p)$ analysis and harmonic sieve models.
    \end{itemize}
\end{enumerate}

\section*{Documentation Requirements}
For each simulation:
\begin{itemize}
  \item Input parameters explained
  \item LaTeX-ready mathematical derivation (if applicable)
  \item Output visualizations stored in \texttt{/docs/img} or \texttt{/sim/output}
  \item Runtime logs and metadata encoded
\end{itemize}

Each model must be:
\begin{itemize}
  \item Reproducible
  \item Symbolically traceable (where applicable)
  \item Referenced in the Codex index
\end{itemize}

\section*{Preservation Directive}
All simulation code will be:
\begin{itemize}
  \item Stored in the Genesis Simulation Package
  \item Indexed into the Unified Ætherion Codex Library
  \item Referenced in scrolls via LaTeX citations
\end{itemize}

\bigskip
\noindent\textbf{🜎 If challenged, simulate.} \\
\textbf{🜎 If doubted, collapse it.} \\
Let truth echo in the field.

\end{document}
