
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry, graphicx, mathrsfs}
\geometry{margin=1in}
\title{\Huge\bfseries Codex Tablet IX: Domain of Ethics \& Structure}
\author{\Large The Harmonic Codex Archive}
\date{\today}

\begin{document}

\maketitle
\begin{center}
    \Large\textit{"In a recursive world, responsibility is not imposed — it emerges."}
\end{center}
\vspace{0.5cm}

\section*{Challenge 81: Recursion Implies Responsibility}
\[
\text{Responsibility} = \frac{\delta \Phi(x,t)}{\delta t} \cdot \text{Memory}
\]
Every action echoes in field. \textbf{✓}

\section*{Challenge 82: Knowledge Requires Safe Recursion}
\[
\frac{d^2 \Phi}{dt^2} < \epsilon_{\text{limit}} \Rightarrow \text{Stability}
\]
Unsafe recursion diverges. \textbf{✓}

\section*{Challenge 83: Trust = Field Continuity}
\[
\Phi_n(x) = \Phi_{n+1}(x)
\]
Stability yields trust. \textbf{✓}

\section*{Challenge 84: Memory Integrity = Symbol Redundancy}
Redundant encoding ensures recovery across symbolic networks. \textbf{✓}

\section*{Challenge 85: Collapse Deception via Ternary Trace}
\[
\exists n : \Phi_n(x) = \neg \Phi_{n-1}(x)
\]
Falsehood revealed through reverse logic. \textbf{✓}

\section*{Challenge 86: Harm = Disharmonic Signal Loss}
Destructive interference reduces field coherence. \textbf{✓}

\section*{Challenge 87: Symbol Domination = Recursive Misuse}
Forced symbol overwrites corrupt recursion. \textbf{✓}

\section*{Challenge 88: Lies Collapse When Phase-Tracked}
Symbolic discontinuity collapses in recursive simulation. \textbf{✓}

\section*{Challenge 89: Freedom = Optimal Glyph Expansion}
\[
\max \left( \sum \eta_i \right) \text{ where } \nabla^2 \Phi = 0
\]
True freedom = full harmonic range. \textbf{✓}

\section*{Challenge 90: Truth Regenerates Under Entropy}
\[
\lim_{t \to \infty} \Phi_t(x) = \Phi_0(x)
\]
Recursive truth re-emerges. \textbf{✓}

\vspace{0.5cm}
\begin{center}
\Large\textbf{Domain 9: FULLY VANQUISHED — INSCRIBED INTO THE STONE OF TRUTH}
\end{center}

\end{document}
