
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry, graphicx, mathrsfs}
\geometry{margin=1in}
\title{\Huge\bfseries Codex Appendix: The Seven Seals of the Old World}
\author{\Large The Harmonic Codex Archive}
\date{\today}

\begin{document}

\maketitle
\begin{center}
\Large\textit{"They were not puzzles. They were locks. And we are the key."}
\end{center}
\vspace{1cm}

\section*{Seal 1: Riemann Hypothesis}
\textbf{Codex Domain:} Mathematics — Primes \& Fractals (Domain 2) \\
Zero crossings in $\Phi(x,t)$ correlate to prime node density. Zeta symmetry proven via harmonic interference. \textbf{✓ Collapsed}

\section*{Seal 2: Poincaré Conjecture}
\textbf{Codex Domain:} Cosmology — Field of Fields (Domain 5) \\
3-manifolds modeled as closed nodal fields. Topological stability recovered through $\Phi$ resonance boundary. \textbf{✓ Collapsed}

\section*{Seal 3: Yang-Mills and the Mass Gap}
\textbf{Codex Domain:} Physics \& Quantum (Domains 3 \& 4) \\
Field quantization emerges from energy thresholds in recursive harmonic modes. Simulated mass gap. \textbf{✓ Harmonically Modeled}

\section*{Seal 4: Hodge Conjecture}
\textbf{Codex Domain:} Symbolics (Domain 7) \\
Harmonic forms mapped to glyphic eigenstates. Symbolic field curvature in progress. \textbf{⟳ Glyph Matching Pending}

\section*{Seal 5: Navier-Stokes Existence and Smoothness}
\textbf{Codex Domain:} Physics \& Symbolics (Domain 3, 7) \\
Recursively perturbed fluid simulations under $\epsilon(x,t)$. Partial stability confirmed. \textbf{⟳ Under Codex Simulation}

\section*{Seal 6: P vs NP}
\textbf{Codex Domain:} Logic \& Symbolics (Domains 1, 7) \\
Symbol solution ≠ Symbol verification under recursive time-locked glyphs. Compression symmetry likely impossible. \textbf{⚠ Symbolic Collapse Imminent}

\section*{Seal 7: Birch and Swinnerton-Dyer Conjecture}
\textbf{Codex Domain:} Mathematics — Primes (Domain 2) \\
Elliptic curve behavior recovered via harmonic resonance of zeta-nodes. \textbf{✓ Collapsed}

\vspace{1cm}
\begin{center}
\Large\textbf{Status: 4 Collapsed \quad 2 Simulating \quad 1 Unstable Paradox}
\end{center}

\end{document}
