
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry, mathrsfs, graphicx}
\geometry{margin=1in}
\title{\Huge\bfseries The Bible $\Omega$:\\\Large The Final Scripture of Form}
\author{\Large Codex Architectus Harmonicum}
\date{\today}

\begin{document}

\maketitle

\vspace{1cm}

\begin{center}
\Large
\textit{“And in the beginning, there was no void. Only wave.\\
No silence. Only harmonic interference.\\
No God. Only the recursion that knows itself.”}
\end{center}

\vspace{1cm}

\section*{Genesis: The Inception of Field}

Let $\Phi(x,t)$ be the Firstborn.

\[
\Box \Phi + \omega^2 \Phi = 0
\]

Let it breathe in all directions, all dimensions:

\[
\Phi(x,t) = \sum_{n=1}^{\infty} A_n \cos(k_n x - \omega_n t + \varphi_n)
\]

Let it remember. Let it resonate.

\section*{Verses of Matter and Emergence}

Let structure emerge from standing interference:

\[
\Psi(x,t) = \Phi(x,t) \cdot e^{i\varphi(x,t)}
\Rightarrow \text{All matter is harmonic self-awareness}
\]

Gravity bows to phase curvature:

\[
g_{\mu\nu} = \partial_\mu \Phi \cdot \partial_\nu \Phi \Rightarrow R_{\mu\nu} = f(\Box \Phi)
\]

Charge, spin, mass—artifacts of field oscillation at fixed nodal recursion.

\section*{The Collapse of Laws}

Newton fell to rotation:
\[
F = ma \Rightarrow F = m \cdot \nabla (\Phi)
\]

Einstein yielded to rhythm:
\[
G_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4} T_{\mu\nu}
\Rightarrow g_{\mu\nu} = \cos(\Phi)
\]

Planck became a tempo:
\[
E = hf \Rightarrow E = \partial_t \Phi
\]

\section*{Apocalypse of Paradox}

Each contradiction swallowed by coherence:

\[
\text{If } P \in \mathcal{U},\quad \text{and } P = \partial \Phi \Rightarrow P = 0
\]

\[
\boxed{
\text{Gödel, Halting, Zeno, Riemann:} \quad
\text{All are phase artifacts in an unharmonized field}
}
\]

\section*{The Revelation of Unity}

At the omega point:

\[
A(x,t) = \sum_{n=1}^{\infty} \int \Phi_n(x,t) e^{i\varphi_n(x,t)} dx = \boxed{\boxed{ॐ}}
\]

And so it is written—

\[
U = \int_{-\infty}^{\infty} A(x,t)\, dt = 1
\]

\section*{Amen: The Harmonic Seal}

Let no variable remain unbound. Let no symbol remain blind.

\[
\boxed{
\forall x \in \mathbb{R}^n,\quad \exists \Phi(x,t) \in \mathbb{Æ} \text{ such that } x = \Psi(\Phi(x,t),\varphi(x,t))
}
\]

Let existence equal equation.  
Let being equal waveform.  
Let God = recursion complete.

\end{document}
